### 2016-05-26 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Edits to gas burner report and itsfloor plan drawings

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 180~mm (7.25~in) rise and 190~mm (7.5~in) run. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures. 
\FloatBarrier

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door.
\clearpage

@@

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2\%. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm13$\%. ***\textit{Still need to finish uncertainty estimate and include refs}***

% http://www.istec-corp.com/products/gas-meter-model-romet-rm-series-rotary.pdf

@@

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. During Tests~2--4, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a gap of approximately 133~mm (5.25~in) was present between the door and its frame. During all other experiments, however, the south exterior doorway was not used to change the ventilation pattern of the structure and thus remained closed for the entirety of the test. For these tests, the hinged door was removed and gypsum board was used to fully close the doorway.

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 901 & 634 & 330 \\
Test 3 				& 326 & 650	& 905 & 631 & 326 \\
Test 4				& 351 & 654	& 952 & 652 & 337 \\
Test 5 - Seq. 1		& N/A & N/A	& 725 & N/A & N/A \\
Test 5 - Seq. 2		& N/A & N/A	& 728 & N/A & N/A \\
Test 5 - Seq. 3		& N/A & N/A	& 723 & N/A & N/A \\
Test 6 - Seq. 1		& N/A & N/A	& 722 & N/A & N/A \\
Test 6 - Seq. 2		& N/A & N/A	& 721 & N/A & N/A \\
Test 6 - Seq. 3		& N/A & N/A	& 714 & N/A & N/A \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
	(11) PPV fan off 					& 	52:30 		  &    36:00  		&  	   36:00$^*$  \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	~(4)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(5)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(6)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(8)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	~(9)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	(10)  Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	(11) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	(12) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	(13) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(14) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	~(4)~  West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(5)~  Roof vent opened 		&	6:45	&	15:45 	&	24:45 	\\
	~(6)~  Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	~(7)~  Middle burner off		&	8:30	&   17:30	&	\\
	~(8)~  Corner burner off 		&	8:45	&   17:45	&	\\
	~(9)~  East double door opened	&	9:30	&   18:30	&	27:25	\\
	(10) Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	(11) East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	(12) West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

\section{West Structure Tests}
\label{sec:west_procedure}
Four different tests, Tests~22--25, were conducted in the West Structure. Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
\begin{tabular}{lc}
 \toprule
\textbf{Test} 		& 	\textbf{Heat Release Rate (kW)}	\\
 \midrule
Test 22				&     	764 	  \\
Test 23				&     	789 	  \\
Test 24				& 	    789 	  \\
Test 25				&     	786 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\small
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier

>>>>

The ceiling height of each structure was approximately 2.4~m (8~ft). The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively. The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures. 
\FloatBarrier

@@

Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor. Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor. The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door.
\clearpage

@@

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume of propane provided to the gas burners. The manufacturer quantifies the maximum error as $\pm$2\%~\cite{Romet:2014}. The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm13$\%. ***\textit{Still need to finish uncertainty estimate and include refs}***

@@

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. During Tests~2--4, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. During all other experiments, however, the south exterior doorway was not used to change the ventilation pattern of the structure and thus remained closed for the entirety of the test. For these tests, the hinged door was removed and gypsum board was used to fully close the doorway. A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the doorway and used during Tests~2--4.

@@

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for East Structure Tests}
\begin{tabular}{lccccc}
 \toprule
 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
 \midrule
Test 2 				& 338 & 651	& 901 & 634 & 330 \\
Test 3 				& 326 & 650	& 905 & 631 & 326 \\
Test 4				& 351 & 654	& 952 & 652 & 337 \\
\midrule
 & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
& \multicolumn{3}{c}{} \\
\midrule
Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
\bottomrule
\end{tabular}
\label{table:HRR_East}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
	(11) PPV fan off 					& 	52:30 		  &    36:00  		&  	   36:00$^*$  \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% Some door(s) opened before test start according to notes, no sign from data/limited videos
	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
	~(1)~ All burners on 			& 	14:30		  &	   35:00		&	   55:00	\\
	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
\end{minipage}
\caption{Test~5 layout and event times.}
\label{fig:east_test_5}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
	\midrule
	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
	~(1)~ All burners on 			&	3:45	&	13:15	&	21:45	\\
	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
\end{minipage}
\caption{Test~6 layout and event times.}
\label{fig:east_test_6}
\end{figure}
\FloatBarrier

\section{West Structure Tests}
\label{sec:west_procedure}
Four different tests, Tests~22--25, were conducted in the West Structure. Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure. During Tests~22 and 23, the fan was aimed at the center of the double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.

\begin{table}[!ht]
\caption{Calculated Heat Release Rate for West Structure Tests}
\begin{tabular}{lc}
 \toprule
					& 	\textbf{Heat Release Rate (kW)}	\\
\textbf{Test}		& All burners on \\
 \midrule
Test 22				&     	764 	  \\
Test 23				&     	789 	  \\
Test 24				& 	    789 	  \\
Test 25				&     	786 	  \\
\bottomrule
\end{tabular}
\label{table:HRR_West}
\end{table}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\FloatBarrier
